The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-10-29 ApJ/ms.tex
Addressing two of the referee's points.

\documentclass[apjl]{emulateapj}
%\documentclass[12pt,preprint]{aastex}

@@

\begin{figure*}
\epsscale{1.15}
\plotone{f1}
\epsscale{1}
  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
    (left to right).  Pictured here are the density-weighted
    projections of density (top), temperature (middle), and
    metallicity (bottom).  Note how the stellar radiative feedback
    from low-mass galaxies reionize the majority of the volume.  The
    metallicity projections are a composite image of metals
    originating from Pop II (blue) and III (red) stars with magenta
    indicating a mixture of the two.}
\end{figure*}

>>>>

%\documentclass[apj]{emulateapj}
\documentclass[12pt,preprint]{aastex}

@@

\begin{figure*}
\epsscale{1.15}
\plotone{f1}
\epsscale{1}
  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
    (left to right).  Pictured here are the density-weighted
    projections of density (top), temperature (middle), and
    metallicity (bottom).  Note how the stellar radiative feedback
    from low-mass galaxies reionize the majority of the volume.  The
    metallicity projections are a composite image of metals
    originating from Pop II (red) and III (blue) stars with magenta
    indicating a mixture of the two.}
\end{figure*}
